Staged Abstract Interpreter

### 2018-08-23 paper/paper.tex
update
reorganize

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
  It is well known that a staged interpreter is a compiler. A nature question is to ask 
  that what would be a staged abstract interpreter and how to obtain it by a mechanized 
  approach.

@@

Not sure how much improvement of performance.

>>>>

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
  It is well known that a staged interpreter is a compiler. A nature question is to ask 
  that what would be if we can stage an abstract interpreter and how to obtain it by a mechanized 
  approach.

@@

IDEA: combining analysis with different sensitivities.

TODO: evaluate the improvement of performance.
